Extending statistical models for source attribution of zoonotic diseases: A study of campylobacteriosis

### 2018-02-05 paper/finalish/article_1023.tex
update figure legends

\begin{figure}
\centering
\includegraphics[width=.9\linewidth]{Figures/FCILandC(5)}
\caption{The posterior mean of samples $F$ with 80\% HPD interval for source: poultry (red), ruminants (green), water (blue) and others (pink) over the rurality scales from highly rural area to main urban area. The samples of attribution probability are generated from the two respective fitted models: the linear model (upper panel) and the categorical model (lower panel), given the sampling distribution of genotypes with evolutionary information (the asymmetric Island model) or without any genetic information (the simple model).}
\label{fig2}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.9\linewidth]{Figures/FCILandC(8)}
\caption{The posterior mean of samples $F$ with 80\% HPD interval for four sources over seven rurality categories after applying our methods to data with the post-intervention time period from 2008 to 2014. The samples of attribution probability are generated from the two respective fitted models -- the linear model (upper panel) and the categorical model (lower panel) -- given the genotype distribution based upon the asymmetric Island model or the simple model.}
\label{fig3}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=.9\linewidth]{Figures/FCILandC(5)}
\caption{Posterior mean attribution probabilities ($F$) with 80\% credible intervals for source: poultry (red), ruminants (green), water (blue) and others (pink) over the rurality scales from highly rural area to main urban area. The samples of attribution probability are generated from the two respective fitted models: the linear model (upper panel) and the categorical model (lower panel), given the sampling distribution of genotypes with evolutionary information (the asymmetric Island model) or without any genetic information (the Dirichlet model).}
\label{fig2}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.9\linewidth]{Figures/FCILandC(8)}
\caption{Posterior mean attribution probabilities ($F$) with 80\% credible interval for four sources over seven rurality categories after applying our methods to data with the post-intervention time period from 2008 to 2014. The samples of attribution probability are generated from the two respective fitted models -- the linear model (upper panel) and the categorical model (lower panel) -- given the genotype distribution based upon the asymmetric Island model or the Dirichlet model.}
\label{fig3}
\end{figure}
